Results (Barcelona)

### 2022-01-17 docs/06_results-bcn.Rmd
Change fig size"

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

@@

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=5}

@@

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

>>>>

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.width=8}

@@

@@

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=5,fig.height=5}
